Eclipse Che for Fair and Easy Education

### 2019-05-04 paper.tex
Raw transcription of Educational Benefits

>>>>

\section{Benefits for Education}
In addition to the previous mentioned benefits, there are more points about Che that are especially important for educational purposes, such as courses in the university, professional school or research departments.
For simplicity I will only elaborate universities, to which I can best relate.
Eclipse Che provides the possibility to learn primary cloud-technologies hands on and in a simple and supportive manner. 
Unfortunetally, these topics are currently not widely teached at university.
Che makes it possible to teach students fundamentals of modern software development.
Depending on the courses subject, one can either provide scalable software or a running environment. 
With fitting material provided, it's easy to learn cloud-native development, DevOps or Cloud-Operations. 
Even complicated topics, like microservices and IoT-applications can easily be adaptet inside Che [21] and performed as for example as group-projects with a common goal. 
The student will need to understand cloud-components aswell as team-work to succeed with Che. 
The produced artifacts can simply be shipped as containers, giving comfortable access to the professor. 
With both the product and the code inside the workspace easily accessible, the professor can grant faster and better feedback for the students, which can have massive impact on learning [1][5].
Additionally, the professor can provide automated end-to-end tests with tools like Jenkins or TravisCI. 
Given such an environment, the student will immideatly get objective feedback, whether their code fulfills the requirements. 
This immediate feedback is a big motivator and has a positive impact on the learning experience [2]. 
With a clear reason on the usefulness of the task, the visible progress and the direct impact of personal effort should lead to intrinsic motivation, which studies show to have a strong effect on education [23]. 
As a requirement, it's necessary to provide a meaningful and fun task. 
Fortunately, such tasks are not that rare in development.  
Other studies have shown that only automated and unified testing is not beneficial to education in general [3]. 
But the tools provided by Che and CI/CD slim down the overhead until both personal feedback and automated can be supplied. 
If the whole classroom utilizes this system, the educator can also monitor who is having trouble in an automated manner. 
With a single investment for the tests, feedback for every student is granted at every time. 
With the single investment of providing a running Che instance (and a short lecture how to use it), feedback on the artifacts and code can be immidieatly granted to every student, without having the overhead of setting up workspaces. 
These investments can be done before the course starts at any time and can be reused.
It's not dependent on the individual students. 
In general, this approach enables studies to be less about the subject, but instead to be about learning the subject. 
I consider this the primary goal of university courses. 
Another benefit for education is about fairness in IT-Education.  
With access to a university Che workspace, every person can develop the same software in the same environment. 
A wellknown problem is the necessity of an IOS-build-device for IOS-appdevelopment.
Students which are limited in their access to the university-laboratory or cannot afford a mac are therefore handicapped.
Another  rising  problem  are  GPU-accelerated  machine learning algorithms. 
Depending on the task, training neural networks can be 20 times faster if a CUDA-compatible graphics card is used. 
The range for these graphiccards start at 300\$ and are therefore not commodity hardware,especially for students.  
While these technologies are great and important for many applications, the required technologies are exclusive due to  their  costs.
This  hindrance  for  education  is  usually adressed  with  IOS-laboratories  and/or  cloud-resources paid for by university. 
The topic of socio-economic factors is beyond the scope of this work, but the impact has been analyzed by the PISA Studies [7], which state that socio-economicly handicapped students fail three times more likely to achieve a basic level of performance.
According to PISA, this rate has not significally changed since the studies started in 2006. 
Germany scored on the impact of socioeconomic-factors on education better than it did in 2006 but is worse than global average [6].
The Mac-Laboratories and rented cloudspace are technically a good attempt at inclusion. 
But students which are required to get to university to do their assignments are 
less  likely  to  do  so.
Making  assignments  mandatory, providing extrinsic motivation [23] has usually a negative impact on the subjective experience.
A different problem comes with machine-learning, which is usually a process of trial and error to some extend.
Long waiting times disconnect the action from the result being not beneficial for the learning process [1][23]. 
One may argue that having this kind of anticipation is extra rewarding and therefore highly motivational.
From my personal experience, working in this modus becomes exhausting after a period of weeks, especially when errors occur. 
I expect this experience to be highly personal. 
I think providing the fastest infrastructure possible, enabling the fastest results, is the better way. 
Making progress slower is much easier than making it faster.  
In addition, the time spent waiting on your machine learning algorithm or moving to the mac-laboratory on weekends is simply dead time. 
It should therefore be minimized.   
With studies showing basics of good learning experiences [2][3] and the impact of motivation [1][23], it is mandatory for institutions to provide the best possible environment. 
While many socio-economic factors cannot be grasped at the university or by the educators, those originating in the students' economic background can be addressed.
Most universities already provide free services, such as software-suites, e-libraries or cloud storage.
Simply providing a technical correct solution (like laboratories) is not enough to provide a good environment.
One student with a better socio-economic background who can afford a 300\$ GPU will have a better baseline for his education. 
This is simply put unfair.
With Che, universities can provide a free, good and accessible development environment for every student.
